---
title: "2025-exeRcise-sheet-3"
author: "Yoomin Lee (12962884)"
date: "2025-05-25"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exercise 1

### d

Advantages of Git: 1. Allows you to track changes and revert to previous
versions if needed. 2. Makes collaboration easy by managing changes from
multiple contributors.

Disadvantages of Git: 1. Can be difficult to learn for beginners due to
unfamiliar commands and concepts. 2. Merge conflicts can be confusing
and hard to resolve.

## Exercise 2

### a

<https://github.com/umin1203/exeRcise-sheet-3>


## Exercise 3

### a

```{r}

library(tidyverse)

pixar_films <- read_csv("data/pixar_films.csv")

pixar_films <- pixar_films %>%
  filter(!is.na(film) & film != "")

unique(pixar_films$film_rating)

pixar_films <- pixar_films %>%
  mutate(film_rating = as.factor(film_rating))

head(pixar_films, 10)

```

The variable `film_rating` contains the following values: G, PG, NA. These represent audience suitability ratings, with G being suitable for all ages, PG suggesting parental guidance. And NA means, that this data is not available. Converting this variable into a factor is appropriate because the ratings are categorical and represent
qualitative levels rather than numerical values.