---
title: "2025-exeRcise-sheet-3"
author: "Yoomin Lee (12962884)"
date: "2025-05-25"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exercise 1

### d

Advantages of Git: 1. Allows you to track changes and revert to previous
versions if needed. 2. Makes collaboration easy by managing changes from
multiple contributors.

Disadvantages of Git: 1. Can be difficult to learn for beginners due to
unfamiliar commands and concepts. 2. Merge conflicts can be confusing
and hard to resolve.

## Exercise 2

### a

<https://github.com/umin1203/exeRcise-sheet-3>


## Exercise 3

### a

```{r}

library(tidyverse)

pixar_films <- read_csv("data/pixar_films.csv")

pixar_films <- pixar_films %>%
  filter(!is.na(film) & film != "")

unique(pixar_films$film_rating)

pixar_films <- pixar_films %>%
  mutate(film_rating = as.factor(film_rating))

head(pixar_films, 10)

```

The variable `film_rating` contains the following values: G, PG, NA. These represent audience suitability ratings, with G being suitable for all ages, PG suggesting parental guidance. And NA means, that this data is not available. Converting this variable into a factor is appropriate because the ratings are categorical and represent
qualitative levels rather than numerical values.


## b

```{r}

pixar_films <- pixar_films %>%
  mutate(series = case_when(
    str_detect(film, "Toy Story") ~ "Toy Story",
    str_detect(film, "Cars") ~ "Cars",
    str_detect(film, "Finding") ~ "Finding",
    str_detect(film, "Incredibles") ~ "Incredibles",
    str_detect(film, "Monsters") ~ "Monsters",
    TRUE ~ NA_character_
  ))

series_df <- pixar_films %>%
  filter(!is.na(series)) %>% 
  group_by(series) %>%
  summarise(
    titles = paste(film, collapse = ", "),
    n_films = n(),
    .groups = "drop"
  )

series_df

```


### c

```{r}
public_response <- read_csv("data/public_response.csv")

cinema_levels <- c("A-", "A", "A+")
public_response <- public_response %>%
  mutate(cinema_score = factor(cinema_score, levels = cinema_levels, ordered = TRUE))

combined_df <- left_join(pixar_films, public_response, by = "film")

head(combined_df,10)
```


### d

```{r}
combined_df <- combined_df %>%
  filter(!is.na(series), !is.na(cinema_score)) %>% 
  arrange(series, release_date) %>%
  mutate(
    series_title = paste(series, film, sep = " - "),
    series_title = fct_inorder(series_title)
  )

ggplot(combined_df, aes(x = series_title, y = cinema_score, fill = series)) +
  geom_col() +
  labs(
    title = "Cinema Score of Pixar Films Grouped by Series",
    x = "Film (Grouped by Series)",
    y = "Cinema Score",
    fill = "Series"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

Based on the bar plot grouped by series and ordered by release date, we observe a general pattern: the scores tend to decline in later films of
a series.


## Exercise 4

### c

-   Dataset Name : Life Expectancy

-   Link :

<https://github.com/owid/owid-datasets/blob/master/datasets/Life%20expectancy%20-%20OECD/Life%20expectancy%20-%20OECD.csv>


### d

How has life expectancy changed over time in South Korea compared to the
Germany?


### e

```{r}
library(tidyverse)

life <- read_csv("data/Life expectancy - OECD.csv")

life_clean <- life %>%
  filter(Entity %in% c("South Korea", "Germany"))

head(life_clean, 5)

```



### f

```{r fig.cap = "Line plot comparing the life expectancy"}
ggplot(life_clean, aes(x = Year, y = `Life Expectancy (OECD)`, color = Entity)) +
  geom_line(size = 1.2) +
  labs(
    title = "Life Expectancy: South Korea vs. Germany",
    subtitle = "South Korea(1970-2015), Germany(1960-2015)",
    x = "Year",
    y = "Life Expectancy (years)",
    caption = "Source: Our World in Data"
  ) +
  theme_minimal()

```

Line plot comparing the life expectancy trends in South Korea and Germany from 1960,70 to 2015. Both countries show significant improvements, with South Korea catching up rapidly since the mid-20th century.
